Modelling the emergence of whisker barrels

### 2020-06-18 paper/briefpaper/brief.tex
Adds text for minor point 6

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\stu}[1]{\textcolor{red}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
% Degrees symbol:
\usepackage{textcomp}

@@

Spatial patterns in neural connectivity provide clues about the constraints
under which brains evolve and develop \citep{purves_iterated_1992}. Perhaps
the most distinctive pattern can be found in the barrel cortex of many rodent
species \citep{woolsey_structural_1970}. The barrels are identifiable soon
after birth in layer 4 of primary somatosensory cortex as dense clusters of
thalamocortical axons, which are enclosed by borders a few neurons thick from
postnatal day 3 \citep{erzurumlu_development_2012}. In the plane tangential to
the cortical surface the barrels constitute a somatotopic map of the whiskers,
with cells within adjacent barrels responding most strongly and quickly to
deflection of adjacent whiskers \citep{armstrong-james_flow_1992}. Barrel
patterning reflects subcortical whisker maps comprising cell aggregates called
barrelettes in the brainstem and barreloids in the thalamus
\citep{ma_barrelettesarchitectonic_1991,van_der_loos_barreloids_1976}.

>>>>

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}

% Colours for revisions:
% Custom colours
\definecolor{revgreen}{rgb}{0.220, 0.463, 0.114}
\definecolor{revblue}{rgb}{0.235, 0.471, 0.847}
\definecolor{revred}{rgb}{1.0, 0.0, 0.0}
\definecolor{revgrey}{rgb}{0.6, 0.6, 0.63}
\definecolor{revcomp}{rgb}{0.0, 0.0, 0.0}
\definecolor{revpurp}{rgb}{0.8, 0.1, 0.8}

% Blue changes are mostly major points 2 (competition mechanism) and 3 (parameter/sensitivity)
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Red for Stuart's updates
\newcommand{\stu}[1]{\textcolor{red}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}

\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
% Degrees symbol:
\usepackage{textcomp}

@@

Spatial patterns in neural connectivity provide clues about the constraints
under which brains evolve and develop \citep{purves_iterated_1992}. Perhaps
the most distinctive pattern can be found in the barrel cortex of many rodent
species \citep{woolsey_structural_1970}. The barrels are identifiable soon
after birth in layer 4 of primary somatosensory cortex as dense clusters of
thalamocortical axons, which are enclosed by borders a few neurons thick from
postnatal day 3 \citep{erzurumlu_development_2012}.
%
% These timings, from erzurumlu_development_2012 originate from
% sehara_neuronal_2011, where they relate to mouse.
\mpsix{In the mouse, axons from the trigeminal ganglion arrive in the principal sensory
  nucleus of the trigeminal nerve (PrV) at E12, then axons from the PrV arrive
  in the ventroposteromedial nucleus of the thalamus (VPM) at E17, then axons
  from the VPM arrive in the cortical plate at E18/P0. Distinct whisker-related
  clusters then become apparent in the PrV at P0-P1, in the VPM at P2-P3, and
  in the cortex at P3-P5} \citep{erzurumlu_development_2012,sehara_neuronal_2011}.
%
In the plane tangential to
the cortical surface the barrels constitute a somatotopic map of the whiskers,
with cells within adjacent barrels responding most strongly and quickly to
deflection of adjacent whiskers \citep{armstrong-james_flow_1992}. Barrel
patterning reflects subcortical whisker maps comprising cell aggregates called
barrelettes in the brainstem and barreloids in the thalamus
\citep{ma_barrelettesarchitectonic_1991,van_der_loos_barreloids_1976}.
